Type Error Telemetry at Scale

### 2023-09-29 programming23/paper.tex
RQs: creator -> session

With this telemetry data, we investigate research questions about
the adoption and benefits of type analysis: \todo{Some of these are flawed. We don't know anything about creators. Adjust
  to match section 5.}
\begin{description}
  \item[RQ1.]
    How many creators use type analysis?
    How often do projects contain modules with different
    analysis modes?
    How often do creators turn analysis off?
  \item[RQ2.]
    For modules that use type analysis:
    which errors arise,
    how do creators respond,
    and which errors tend to persist despite subsequent edits?
  \item[RQ3.]
    What impact does type analysis have on the number of \FS{}
    errors?
    For example, do \FS{} errors pile up in unanalyzed projects?
\end{description}

@@

  \item
    An available dataset of over 1.5 million telemetry records
    and scripts to analyze them.
    \emph{We intend to submit this in an artifact.}

@@

\begin{description}
  \item[How many creators choose to use type analysis?]
    A mere \pct{10} of sessions (and of telemetry records overall) opt-in to
    type checking~(\cref{f:dataset-overview}).
    Most of these use \mnonstrict{} mode, and fewer than \pct{1}
    use \mstrict{} mode.

@@

  \item[How often do creators turn analysis off?]
    Sessions rarely disable type analysis after opting in.
    Only 233 of the \nK{340} sessions ($<\pct{0.07}$)
    switch to a weaker mode.
    Most of these (\pct{75}) downgrade from \mstrict{} to
    \mnonstrict{} % BEN: confirm!
    rather than from \mnonstrict{} mode.
    %% FILL more insight if we match upgrades + downgrades in session?

@@

      \item[- How do creators respond? Which errors persist through edits?]
        Sessions typically fix analysis errors.
        With few exceptions, increases and decreases in the number of errors
        balance out~(\cref{f:error-changes,t:type-error-survival,}).
        Even in \mnocheck{}, most edits that overlap with syntax errors
        remove at least one error~(\pct{67}) rather than increase or maintain
        the total.
        The errors that most often survive edits are due to
        inference at a binary operation,
        sending \code{self} to a function that does not expect it,
        and failure to unpack an optional value.
        But the first two seldom arise, and the third is something creators
        might reasonably ignore while prototyping.

>>>>

With this telemetry data, we investigate research questions about
the adoption and benefits of type analysis:
\begin{description}
  \item[RQ1.]
    How many sessions use type analysis?
    How often do projects contain modules with different
    analysis modes?
    How often do sessions turn analysis off?
  \item[RQ2.]
    For modules that use type analysis:
    which errors arise,
    how do sessions respond,
    and which errors tend to persist despite subsequent edits?
  \item[RQ3.]
    What impact does type analysis have on the number of \FS{}
    errors?
    For example, do \FS{} errors pile up in unanalyzed projects?
\end{description}

@@

  \item
    An available dataset of over 1.5 million telemetry records
    and scripts to analyze them.
    \emph{We intend to submit these in an artifact.}

@@

\begin{description}
  \item[How many sessions use type analysis?]
    A mere \pct{10} of sessions (and of telemetry records overall) opt-in to
    type checking~(\cref{f:dataset-overview}).
    Most of these use \mnonstrict{} mode, and fewer than \pct{1}
    use \mstrict{} mode.

@@

  \item[How often do sessions turn analysis off?]
    Sessions rarely disable type analysis after opting in.
    Only 233 of the \nK{340} sessions ($<\pct{0.07}$)
    switch to a weaker mode.
    Most of these (\pct{75}) downgrade from \mstrict{} to
    \mnonstrict{} % BEN: confirm!
    rather than from \mnonstrict{} mode.
    %% FILL more insight if we match upgrades + downgrades in session?

@@

      \item[- How do sessions respond? Which errors persist through edits?]
        Sessions typically fix analysis errors.
        With few exceptions, increases and decreases in the number of errors
        balance out~(\cref{f:error-changes,t:type-error-survival,}).
        Even in \mnocheck{}, most edits that overlap with syntax errors
        remove at least one error~(\pct{67}) rather than increase or maintain
        the total.
        The errors that most often survive edits are due to
        inference at a binary operation,
        sending \code{self} to a function that does not expect it,
        and failure to unpack an optional value.
        But the first two seldom arise, and the third is something creators
        might reasonably ignore while prototyping.
